Thesis outline

### 2017-07-19 KellyDouglass/Thesis/Thesis_sections/Conclusion.tex
Updated text in small scale environment chapter

We find that the large-scale environment influences the chemical evolution of 
dwarf galaxies by estimating the gas-phase oxygen (O/H) and nitrogen (N/H) 
abundances and the N/O ratio of star-forming dwarf galaxies in SDSS DR7 using 
the Direct $T_e$ method and spectroscopic line flux measurements as reprocessed 
in the MPA-JHU catalog \citep[Douglass et al., 2017, in prep]{Douglass17a,
Douglass17b}.  Due to the minimum redshift limit for detecting the [\ion{O}{2}] 
$\lambda$3727 emission line in SDSS DR7 spectra, only 135 star-forming dwarf 
galaxies are available for analysis with the Direct $T_e$ method.  With this 
sample, we see no difference in the metallicity (O/H) between dwarf galaxies in 
voids and denser regions \citep{Douglass17a}.  Upon closer inspection, we find 
minor shifts in the distributions of gas-phase chemical abundances for void 
dwarf galaxies when compared to dwarf galaxies in denser regions: star-forming 
void dwarf galaxies have higher oxygen abundances (O/H), lower nitrogen 
abundances (N/H), and lower N/O ratios \citep{Douglass17b}.

>>>>

We find that the large-scale environment influences the chemical evolution of 
dwarf galaxies by estimating the gas-phase oxygen (O/H) and nitrogen (N/H) 
abundances and the N/O ratio of star-forming dwarf galaxies in SDSS DR7 using 
the Direct $T_e$ method and spectroscopic line flux measurements as reprocessed 
in the MPA-JHU catalog \citep{Douglass17a,Douglass17b,Douglass17c}.  Due to the 
minimum redshift limit for detecting the [\ion{O}{2}] $\lambda$3727 emission 
line in SDSS DR7 spectra, only 135 star-forming dwarf galaxies are available for 
analysis with the Direct $T_e$ method.  With this sample, we see no difference 
in the metallicity (O/H) between dwarf galaxies in voids and denser regions 
\citep{Douglass17a}.  Upon closer inspection, we find minor shifts in the 
distributions of gas-phase chemical abundances for void dwarf galaxies when 
compared to dwarf galaxies in denser regions: star-forming void dwarf galaxies 
have higher oxygen abundances (O/H), lower nitrogen abundances (N/H), and lower 
N/O ratios \citep{Douglass17b}.

### 2017-07-19 KellyDouglass/Thesis/Thesis_sections/GV.tex
Updated text in small scale environment chapter

The SDSS Data Release 7 \citep[DR7;][]{Abazajian09} is a wide-field multi-band 
imaging and spectroscopic survey that uses drift scanning to map approximately 
one-quarter of the northern sky.  A dedicated 2.5-meter telescope at the Apache 
Point Observatory in New Mexico takes photometric data in the five-band SDSS 
system --- $u$, $g$, $r$, $i$, and $z$ \citep{Fukugita96,Gunn98}.  Galaxies with 
a Petrosian $r$-band apparent magnitude $m_r < 17.77$ are selected for 
spectroscopic analysis \citep{Lupton01,Strauss02}.  Gas-phase chemical 
abundances are calculated via the Direct $T_e$ method using emission-line fluxes 
measured by the MPA-JHU catalog\footnote{Available at 
\url{http://www.mpa-garching.mpg.de/SDSS/DR7}} and published in Douglass et al. 
(2017, submitted).  The large-scale environment of the galaxies is based on the 
void catalog compiled by \cite{Pan12}.  This void catalog is constructed from 
SDSS DR7 using the VoidFinder algorithm of \cite{Hoyle02}.  Galaxies which are 
located within the identified voids are labeled as void galaxies; those which do 
not reside in a void are designated as wall galaxies.  Because the minimum 
diameter of a void is defined as 10 \hMpc , the large-scale environment of 
galaxies within 5 \hMpc of the edge of the SDSS DR7 footprint cannot be 
described, so their environment is labeled as unknown.

@@

Estimates of the gas-phase chemical abundances of galaxies probe their 
integrated star formation histories, which can provide insight into the 
enrichment of the ISM and CGM.  A few of the galaxies for which Douglass et al. 
(2017, submitted) are able to estimate metallicities reside in the green valley.  
When compared with the metallicities of galaxies in the blue sequence and red 
cloud, Fig. \ref{fig:Z_hist} shows that the green valley galaxies have higher 
nitrogen abundances than star-forming galaxies in the blue sequence (and some of 
the red cloud).  With oxygen abundances that fall within the same range as the 
other two galaxy populations, this shift causes the N/O ratio to be much higher 
in green valley galaxies than in the blue sequence.  Our interpretation of this 
shift is described in Sec. \ref{sec:discussion_GV}.

@@

Fig. \ref{fig:Mr_bin} shows a higher fraction of faint wall galaxies than faint 
void galaxies are in the green valley.  This would indicate that void galaxies 
are slightly behind wall galaxies in their evolution, matching predictions based 
on the $\Lambda$CDM cosmology.  These results also coincide with the 
observations of \cite{Douglass17b} and Douglass \& Vogeley (2017, submitted).  
They find that, for dwarf galaxies ($M_r > -17$), those which exist in voids may 
have commenced their star formation at a later time.  The higher fraction of 
wall dwarf galaxies in the green valley might also point to an environmental 
influence on the reason for transitioning through the green valley, such as ram 
pressure stripping, which would occur much less frequently in the void 
environment.  However, the existence of void galaxies in the green valley 
indicate that galaxy interactions cannot be the only star formation quenching 
mechanism.

@@

There is a higher fraction of faint wall galaxies than faint void galaxies in 
the green valley.  In conjunction with the conclusions of \cite{Douglass17b} and 
Douglass et al. (2017, submitted), this indicates that void dwarf galaxies are 
less evolved than dwarf galaxies in denser environments.  It would be beneficial 
to investigate the small-scale ($\sim$1 \hMpc) environment of galaxies in the 
green valley, to determine if any interactions are responsible for the 
transitional state.

>>>>

The SDSS Data Release 7 \citep[DR7;][]{Abazajian09} is a wide-field multi-band 
imaging and spectroscopic survey that uses drift scanning to map approximately 
one-quarter of the northern sky.  A dedicated 2.5-meter telescope at the Apache 
Point Observatory in New Mexico takes photometric data in the five-band SDSS 
system --- $u$, $g$, $r$, $i$, and $z$ \citep{Fukugita96,Gunn98}.  Galaxies with 
a Petrosian $r$-band apparent magnitude $m_r < 17.77$ are selected for 
spectroscopic analysis \citep{Lupton01,Strauss02}.  Gas-phase chemical 
abundances are calculated via the Direct $T_e$ method using emission-line fluxes 
measured by the MPA-JHU catalog\footnote{Available at 
\url{http://www.mpa-garching.mpg.de/SDSS/DR7}} and published in 
\cite{Douglass17c}.  The large-scale environment of the galaxies is based on the 
void catalog compiled by \cite{Pan12}.  This void catalog is constructed from 
SDSS DR7 using the VoidFinder algorithm of \cite{Hoyle02}.  Galaxies which are 
located within the identified voids are labeled as void galaxies; those which do 
not reside in a void are designated as wall galaxies.  Because the minimum 
diameter of a void is defined as 10 \hMpc , the large-scale environment of 
galaxies within 5 \hMpc of the edge of the SDSS DR7 footprint cannot be 
described, so their environment is labeled as unknown.

@@

Estimates of the gas-phase chemical abundances of galaxies probe their 
integrated star formation histories, which can provide insight into the 
enrichment of the ISM and CGM.  A few of the galaxies for which 
\cite{Douglass17c} are able to estimate metallicities reside in the green 
valley.  When compared with the metallicities of galaxies in the blue sequence 
and red cloud, Fig. \ref{fig:Z_hist} shows that the green valley galaxies have 
higher nitrogen abundances than star-forming galaxies in the blue sequence (and 
some of the red cloud).  With oxygen abundances that fall within the same range 
as the other two galaxy populations, this shift causes the N/O ratio to be much 
higher in green valley galaxies than in the blue sequence.  Our interpretation 
of this shift is described in Sec. \ref{sec:discussion_GV}.

@@

Fig. \ref{fig:Mr_bin} shows a higher fraction of faint wall galaxies than faint 
void galaxies are in the green valley.  This would indicate that void galaxies 
are slightly behind wall galaxies in their evolution, matching predictions based 
on the $\Lambda$CDM cosmology.  These results also coincide with the 
observations of \cite{Douglass17b} and \cite{Douglass17c}.  They find that, for 
dwarf galaxies ($M_r > -17$), those which exist in voids may have commenced 
their star formation at a later time.  The higher fraction of wall dwarf 
galaxies in the green valley might also point to an environmental influence on 
the reason for transitioning through the green valley, such as ram pressure 
stripping, which would occur much less frequently in the void environment.  
However, the existence of void galaxies in the green valley indicate that galaxy 
interactions cannot be the only star formation quenching mechanism.

@@

There is a higher fraction of faint wall galaxies than faint void galaxies in 
the green valley.  In conjunction with the conclusions of \cite{Douglass17b} and 
\cite{Douglass17c}, this indicates that void dwarf galaxies are less evolved 
than dwarf galaxies in denser environments.  It would be beneficial to 
investigate the small-scale ($\sim$1 \hMpc) environment of galaxies in the green 
valley, to determine if any interactions are responsible for the transitional 
state.

### 2017-07-19 KellyDouglass/Thesis/Thesis_sections/Introduction.tex
Updated text in small scale environment chapter

% Void galaxies
\begin{figure}
    \includegraphics[width=0.9\textwidth]{Images/Intro/VoidFinder}
    \caption[Sky map highlighting voids and void galaxies]{A 10 \hMpc slice of 
    SDSS DR7 \citep[Fig. 1]{Moorman14} with void regions highlighted in blue 
    circles.  Void galaxies are shown as red points while wall galaxies are 
    black.  Existing in the cosmological voids (space between the galactic 
    filaments), void galaxies are though to demonstrate the fundamental 
    characteristics of galactic evolution.}
\end{figure}

>>>>

% Void galaxies
\begin{figure}
    \includegraphics[width=0.9\textwidth]{Images/Intro/VoidFinder}
    \caption[Sky map highlighting voids and void galaxies]{A 10 \hMpc slice of 
    SDSS DR7 \citep[Fig. 1]{Moorman14} with void regions highlighted in blue 
    circles.  Void galaxies are shown as red points while wall galaxies are 
    black.  Existing in the cosmological voids (space between the galactic 
    filaments), void galaxies are thought to demonstrate the fundamental 
    characteristics of galactic evolution.}
\end{figure}

### 2017-07-19 KellyDouglass/Thesis/Thesis_sections/Paper1.tex
Updated text in small scale environment chapter

The effects of the void environment should be most obvious in the dwarf 
galaxies.  Dwarf galaxies are sensitive to many astrophysical effects, including 
cosmological reionization, internal feedback from supernova and photoheating 
from star formation, external effects from tidal interactions and ram pressure 
stripping, small-scale details of dark matter halo assembly, and properties of 
dark matter. Many of these effects have been invoked to attempt to resolve the 
discrepancy between the mass function of galaxy halos predicted by $\Lambda$CDM 
and the observed, much smaller density of dwarf galaxies observed in voids (see, 
e.g., \cite{Kravtsov09} for a review).  It is critical to explore dwarfs in 
voids to complement studies of dwarfs in groups and clusters because the 
assembly histories of low-mass galaxies are predicted to be very different 
\citep[e.g.,][]{Gao07, Lackner12} and observations to date show that the 
properties of dwarfs vary dramatically with environment \citep[e.g.,][]{Ann08, 
Geha12}.  Diffuse cold-mode accretion, rather than mergers, has been suggested 
to be the dominant mechanism for growing dark matter halos in voids 
\citep[e.g.,][]{Keres05, Fakhouri09}.  Late-time gas accretion may be possible 
in voids if void galaxies retain a baryonic reservoir up to the present epoch.  
Thus, these few, lonely, faint galaxies test important features of the structure 
formation model and our understanding of galaxy formation ``gastrophysics.''

>>>>

The effects of the void environment should be most obvious in the dwarf 
galaxies.  Dwarf galaxies are sensitive to many astrophysical effects, including 
cosmological reionization, internal feedback from supernovae and photoheating 
from star formation, external effects from tidal interactions and ram pressure 
stripping, small-scale details of dark matter halo assembly, and properties of 
dark matter. Many of these effects have been invoked to attempt to resolve the 
discrepancy between the mass function of galaxy halos predicted by $\Lambda$CDM 
and the observed, much smaller density of dwarf galaxies observed in voids (see, 
e.g., \cite{Kravtsov09} for a review).  It is critical to explore dwarfs in 
voids to complement studies of dwarfs in groups and clusters because the 
assembly histories of low-mass galaxies are predicted to be very different 
\citep[e.g.,][]{Gao07, Lackner12} and observations to date show that the 
properties of dwarfs vary dramatically with environment \citep[e.g.,][]{Ann08, 
Geha12}.  Diffuse cold-mode accretion, rather than mergers, has been suggested 
to be the dominant mechanism for growing dark matter halos in voids 
\citep[e.g.,][]{Keres05, Fakhouri09}.  Late-time gas accretion may be possible 
in voids if void galaxies retain a baryonic reservoir up to the present epoch.  
Thus, these few, lonely, faint galaxies test important features of the structure 
formation model and our understanding of galaxy formation ``gastrophysics.''
